Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-08-07 notes.tex
made some obvious simplifications

			    &= \left\{\frac{2}{N}\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}

@@

G_H(\vec r, \omega) = \frac{1}{N}\sum_{\vec k} e^{i\vec{k}.\vec{r}}G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}e^{i\vec{k}.\vec{r}}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}~.

@@

	G_H(\vec r = 0, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}

@@

A_{H}(\vec{k},\omega) &=& -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{1}{\pi} \textrm{Im}\left[ (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right]~,\nonumber\\
A_{H}(\vec{r}=0,\omega) &=& -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = -\frac{1}{N\pi} \textrm{Im}\left[\sum_{\vec{k}} (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right] = ~-\frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)~.
We can again use eqs.\eqref{2dsquaretb},\eqref{local_gf} and \eqref{nn_gf} to obtain the spectral functions  $A_{H} (\vec{k},\omega)$ and $A_{H} (\vec{r}=0,\omega)$ for the Hubbard model on the 2D square lattice.

>>>>

			    &= \left\{\frac{2}{N}\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}\\
			    &= \frac{N}{2}\left\{\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{1}{w}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}\\

@@

	G_H(\vec r, \omega) = \frac{1}{\sqrt N}\sum_{\vec k} e^{i\vec{k}.\vec{r}}G_H(\vec k, \omega) &= \frac{1}{\sqrt N}\sum_{\vec k}e^{i\vec{k}.\vec{r}}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\\
												     &= \frac{\sqrt N}{2}\sum_{\vec k}e^{i\vec{k}.\vec{r}}\left\{\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{1}{w}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}

@@

	G_H(\vec r = 0, \omega) = \frac{1}{\sqrt N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{\sqrt N}\sum_{\vec k}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}

@@

A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{1}{\pi} \textrm{Im}\left[ (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right]\\
A_{H}(\vec{r}=0,\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = -\frac{1}{\sqrt N\pi} \textrm{Im}\left[\sum_{\vec{k}} (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right] = -\frac{1}{\sqrt N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)
We can again use eqs.\eqref{2dsquaretb}, \eqref{local_gf} and \eqref{nn_gf} to obtain the spectral functions  $A_{H} (\vec{k},\omega)$ and $A_{H} (\vec{r}=0,\omega)$ for the Hubbard model on the 2D square lattice.
